Meta-analysis

### 2021-01-20 04_MetaAnalysis.Rmd
Edit estimates table; and apply stylr

# Data
load("cache/PrepData.Rdata")
```

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~1 | id), 
   struct = "UN",
   control=list(optimizer="optim"),
   data = PM_MB_dat
)

@@

Lets try the model with an implied simpler variance-covariance matrix "compound symetry" ("CS") to examine if unstructured matrix is suitable.
```{r}
PM_mv_cs <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~1 | id), 
   struct = "CS",
   control=list(optimizer="optim"),
   data = PM_MB_dat
)

@@

```{r metafor_results}

k5 <- as.data.frame(table(PM_MB_dat$trial, PM_MB_dat$spray_management)) %>%
   filter(Freq !=0)%>%
   group_by(Var2)%>%
   summarise(n())%>%
   pull()

results_mv <- data.frame(N = PM_mv$g.levels.k,
                         k = k5,
                         Effect = round(PM_mv$b,4),
                         se = round(PM_mv$se,4),
                         CI_lower = round(PM_mv$ci.lb,4),
                         CI_upper = round(PM_mv$ci.ub,4),
                         z_val = round(PM_mv$zval,4),
                         p_val = reportP(PM_mv$pval,AsNumeric = TRUE),
                         row.names = c("Intercept",
                                       "$Early_{single}$",
                                       "$Recommended_{single}$",
                                       "$Recommended_{plus}$",
                                       "$Late_{single}$",
                                       "$Late_{plus}$"))

colnames(results_mv)[c(1:4,6:9)] <- c("Treatment","$N$", "$k$","$\\mu$","$CI_{L}$","$CI_{U}$", "$Z$","$P$")

kable(results_mv[,2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table ##: Mean effect size of five spray schedule treatments on mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia. Effect sizes were estimated from the network meta-analysis of data obtained from grey literature reports. Intercept indicates the mean of the no spray control and the treatments show the mean difference to the intercept")

@@

```{r metafor_plot}
results_mv %>%
   filter(Treatment != "control") %>%
   mutate(Treatment = factor(Treatment, levels = rev(
      c(
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, `$\\mu$`)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_hline(yintercept = 0) +
   geom_point(aes(size = 1 / se), shape = 15) +
   geom_linerange(aes(ymin = `$CI_{L}$`, ymax = `$CI_{U}$`)) +
   coord_flip() +
   #ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")+
   ylab(expression(paste("Mean yield difference to control (t ha" ^ -1,")",sep = ""))) +
   scale_x_discrete(
      "Moderator variable",
      labels = c(
         expression("Late"["plus"]),
         expression("Late"["single"]),
         expression("Recommended"["plus"]),
         expression("Recommended"["single"]),
         expression("Early"["single"])
      )
   )
ggsave("paper/figures/Fig2_means_difference.png")
```

@@

```{r PM_Mv_Contrast}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
contrast_Ssum <- simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
contrast_Ssum
```

These contrasts can be viewed in a plot
```{r plotContrasts}
par(mar = c(5, 13, 4, 2) + 0.1)
plot(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), yaxt='n')
axis(2, at = seq_along(contrast_Ssum$contrast), labels = rev(contrast_Ssum$contrast), las=2, cex.axis = 0.8)
```

@@

### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
index1 <- PM_MB_dat %>%
   mutate(ID = seq_along(trial_ref)) %>%
   mutate(spray_management = 
             factor(spray_management, 
                    levels = c("Early","Late","Recommended",
                    "Recommended_plus","Late_plus"))) %>%
   arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
   mutate(ID2 = order(ID))%>%
   pull(ID2)

### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
### this list can be used below to reference where to plot each variable
rows1 <- forest_rows(head_row = 186, 
                     ord_var = PM_MB_dat$spray_management, 
                     index = index1, 
                     gap = 5, 
                     row_offset = -2)

### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
                    x = c(coef(PM_mv)[1],coef(PM_mv)[1] + coef(PM_mv)[2:6]),
                    ci.lb = c(PM_mv$ci.lb[1],PM_mv$ci.lb[1] +PM_mv$ci.lb[2:6]),
                    ci.ub = c(PM_mv$ci.ub[1],PM_mv$ci.ub[1] +PM_mv$ci.ub[2:6]))[c(2,5,3,4,6,1),]
polys$rows <- rows1$pred_row - 1.5

forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                #order = "fit",
                rows = rows1$trows-1.5,
                ilab = cbind(PM_MB_dat$year, 
                             PM_MB_dat$row_spacing, PM_MB_dat$host_genotype, PM_MB_dat$dose),
                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4)+1,
                slab = NA, 
                xlim = c(-2, 4),
                ylim = c(5,190),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.2,0.15,0.2),
                at = seq(-0.5,3, 0.5))

>>>>

# Data
load("cache/PrepData.Rdata"
)
```

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_MB_dat
)

@@

Lets try the model with an implied simpler variance-covariance matrix "compound symetry" ("CS") to examine if unstructured matrix is suitable.
```{r}
PM_mv_cs <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "CS",
   control = list(optimizer = "optim"),
   data = PM_MB_dat
)

@@

```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_MB_dat$trial, PM_MB_dat$spray_management)) %>%
   filter(Freq != 0) %>%
   group_by(Var2) %>%
   summarise(n()) %>%
   pull()

# create data.frame
results_mv <- data.frame(
   N = PM_mv$g.levels.k,
   k = k5,
   Effect = round(PM_mv$b, 4),
   se = round(PM_mv$se, 4),
   CI_lower = round(PM_mv$ci.lb, 4),
   CI_upper = round(PM_mv$ci.ub, 4),
   z_val = round(PM_mv$zval, 4),
   p_val = reportP(PM_mv$pval, AsNumeric = TRUE)
)

# adjust estimates to show absolute means
results_mv <-
   results_mv[2:6, ] %>%
   mutate(Effect = Effect + results_mv$Effect[1]) %>%
   mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
   mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
   bind_rows(results_mv[1, ]) %>%
   mutate(index = c(2:6, 1)) %>%
   arrange(index)

# rename colnames to give table headings
colnames(results_mv)[c(1:4, 6:9)] <-
   c("Treatment",
     "$N$",
     "$k$",
     "$\\mu$",
     "$CI_{L}$",
     "$CI_{U}$",
     "$Z$",
     "$P$")

# provide rownames for each moderator variable
row.names(results_mv) <- c(
   "Intercept / No Spray control",
   "$Early_{single}$",
   "$Recommended_{single}$",
   "$Recommended_{plus}$",
   "$Late_{single}$",
   "$Late_{plus}$"
)

kable(results_mv[, 2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table ##: Estimated mean mungbean yields for each spray schedule treatment used for mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia. Yield estimates were calculated from the network meta-analysis of data obtained from grey literature reports. Z and P values indicate statistical significance in comparison to the intercept.")

@@

```{r metafor_plot}
results_mv %>%
   filter(Treatment != "control") %>%
   mutate(Treatment = factor(Treatment, levels = rev(
      c(
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, `$\\mu$`)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_hline(yintercept = 0) +
   geom_point(aes(size = 1 / se), shape = 15) +
   geom_linerange(aes(ymin = `$CI_{L}$`, ymax = `$CI_{U}$`)) +
   coord_flip() +
   #ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")+
   ylab(expression(paste(
      "Mean yield difference to control (t ha" ^ -1, ")", sep = ""
   ))) +
   scale_x_discrete(
      "Moderator variable",
      labels = c(
         expression("Late"["plus"]),
         expression("Late"["single"]),
         expression("Recommended"["plus"]),
         expression("Recommended"["single"]),
         expression("Early"["single"])
      )
   )
ggsave("paper/figures/Fig2_means_difference.png",
       height = 3,
       dpi = 500)
```

@@

```{r PM_Mv_Contrast}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
summary(glht(PM_mv, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), test = adjusted("none"))
contrast_Ssum <-
   simple_summary(summary(glht(PM_mv, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))
contrast_Ssum
```

These contrasts can be viewed in a plot
```{r plotContrasts}
par(mar = c(5, 13, 4, 2) + 0.1)
plot(glht(PM_mv, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), yaxt = 'n')
axis(
   2,
   at = seq_along(contrast_Ssum$contrast),
   labels = rev(contrast_Ssum$contrast),
   las = 2,
   cex.axis = 0.8
)
```

@@

### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
index1 <- PM_MB_dat %>%
   mutate(ID = seq_along(trial_ref)) %>%
   mutate(spray_management =
             factor(
                spray_management,
                levels = c(
                   "Early",
                   "Late",
                   "Recommended",
                   "Recommended_plus",
                   "Late_plus"
                )
             )) %>%
   arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
   mutate(ID2 = order(ID)) %>%
   pull(ID2)

### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
### this list can be used below to reference where to plot each variable
rows1 <- forest_rows(
   head_row = 186,
   ord_var = PM_MB_dat$spray_management,
   index = index1,
   gap = 5,
   row_offset = -2
)

### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
polys <- data.frame(
   ref = change_labels(names(coef(PM_mv))),
   x = c(coef(PM_mv)[1], coef(PM_mv)[1] + coef(PM_mv)[2:6]),
   ci.lb = c(PM_mv$ci.lb[1], PM_mv$ci.lb[1] + PM_mv$ci.lb[2:6]),
   ci.ub = c(PM_mv$ci.ub[1], PM_mv$ci.ub[1] + PM_mv$ci.ub[2:6])
)[c(2, 5, 3, 4, 6, 1), ]
polys$rows <- rows1$pred_row - 1.5

forest1  <- metafor::forest(
   PM_mv,
   cex = 1.15 ,
   width = 5,
   #order = "fit",
   rows = rows1$trows - 1.5,
   ilab = cbind(
      PM_MB_dat$year,
      PM_MB_dat$row_spacing,
      PM_MB_dat$host_genotype,
      PM_MB_dat$dose
   ),
   ilab.xpos = c(-2.35, -2.1, -1.8, -1.4) + 1,
   slab = NA,
   xlim = c(-2, 4),
   ylim = c(5, 190),
   xlab = "Grain yield mean difference",
   addfit = FALSE,
   efac = c(0.2, 0.15, 0.2),
   at = seq(-0.5, 3, 0.5)
)
